\section{Game Theoretic approach to Tree-Depth}

\subsection{Definition of the game}
\paragraph{}
The k-step selection-deletion game is played by Alice and Bob on a graph G. The game is played by turns as follows:
\begin{itemize}
  \item First, Alice selects a connected component of the graph, and the rest of the components are deleted.
  \item Then, Bob deletes a node from the remaining graph.
\end{itemize}

If Bob deletes the last node at the k-th round or earlier, he is said to win the k-step selection-deletion game. Otherwise, Alice wins.

\begin{lemma}
Let G be a graph and let F be a rooted forest of height at most t such that G $\subseteq$ clos(F). Then Bob has a winning strategy for the (t+1)-step selection-deletion game.
\end{lemma}
\begin{proof}
Because of lemma~\ref{lema:min-ET} we know an elimination forest Y exists where height(Y) $\leq$ height(F).
We will proof this by induction on the height of Y.
\begin{itemize}
  \item \textbf{Base case}: If height(Y) = 0, then every component of G will have a single vertex, so it's clear that Bob will win in the 1-step selection-deletion game.
  \item \textbf{Induction}: Let $G_i \subseteq G$ be the component Alice chooses, then $Y_i$ exists such that $Y_i$ is a component of Y, $G_i \subseteq clos(Y_i)$ and obviously $height(Y_i) \leq height(Y)$. Bob will delete the root of $Y_i$
  
  Assume we have a winning strategy for Bob in t steps for every graph that is contained in an elimination forest of height t-1.
\end{itemize}
\end{proof}